---
title: 'Contextual Familiarity Rescues the Cost of Switching: Experiment 1'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
#Load in libraries 
library(tidyverse)
library(rio)
library(plyr)
library(dplyr)
library(fs)
library(lme4)
library(lmerTest)
library(psych)
options(scipen=999)
library(ggplot2)
library(sjPlot)
library(stats)
library(plotrix)
```

#ENCODING

```{r}
#loading in data 

switch11 <- import("switchfreq_11_main_raw_21_02_21.csv")

#filter out subjects who are not included in final sample 
# Create a vector of subjects to exclude
excluded_subjects <- c(
  '135805', '141694', '149968', '154129', '155302', '156577', '156625', '156892',
  '156919', '156967', '157111', '157219', '157225', '157228', '157243', '157426',
  '157441', '157522', '157552', '157576', '157585', '157681', '742243851', 
  '157843', '742243853', '157771'
)

# Filter out subjects in one step
switch11_use <- switch11 %>% 
  filter(!subject %in% excluded_subjects)

  
#filter out the math distractor task to include only the encoding data 
sf11_total_encodingonly <-  switch11_use %>% 
  filter(str_detect(trialcode, "image"))


```



```{r}

#add in columns to data set 
sf11_total_encodingonly_new <- sf11_total_encodingonly %>% 
 mutate(blocknum_contin = case_when(blocknum == "11" ~ "1",
                                         blocknum == "15" ~"2",
                                         blocknum == "19" ~"3",
                                         blocknum == "23" ~"4",
                                      blocknum == "27" ~ "5",
                                         blocknum == "31" ~"6",
                                         blocknum == "35" ~"7",
                                         blocknum == "39" ~"8")) %>% 
  mutate(list_half = case_when(trialnum == "1" ~ "first_half",
                                         trialnum == "2" ~"first_half",
                                         trialnum == "3" ~"first_half",
                                         trialnum == "4" ~"first_half",
                                         trialnum == "5" ~ "first_half",
                                         trialnum == "6" ~"first_half",
                                         trialnum == "7" ~"first_half",
                                         trialnum == "8" ~"first_half",
                                         trialnum == "9" ~"first_half",
                                         trialnum == "10" ~"first_half",
                                         trialnum == "11" ~"first_half",
                                         trialnum == "12" ~ "first_half",
                                         trialnum == "13" ~"second_half",
                                         trialnum == "14" ~"second_half",
                                         trialnum == "15" ~"second_half",
                                          trialnum == "16" ~"second_half",
                                         trialnum == "17" ~"second_half",
                                         trialnum == "18" ~"second_half",
                                          trialnum == "19" ~"second_half",
                                         trialnum == "20" ~"second_half",
                                         trialnum == "21" ~"second_half",
                                          trialnum == "22" ~"second_half",
                                         trialnum == "23" ~"second_half",
                                         trialnum == "24" ~"second_half")) %>% 
  mutate(condition_control = case_when(condition == "cont_mid" ~ "no switch",
                                         condition == "cont_high" ~"no switch",
                                         condition == "high" ~"switch",
                                         condition == "mid" ~"switch")) %>% 
  mutate(condition_mh = case_when(condition == "cont_mid" ~ "mid",
                                         condition == "cont_high" ~"high",
                                         condition == "high" ~"high",
                                         condition == "mid" ~"mid")) %>% 
    mutate(pool_number = case_when(word_enc == "ACORN"~ 1, 
word_enc == "ANCHOR"~	2,
word_enc =="APPLE"	~3,
word_enc =="APRON"	~4, 
word_enc =="ARROW"~	5,
word_enc =="ATLAS"~	6,
word_enc =="BACON"~	7,
word_enc =="BAKER"~	8,
word_enc =="BANDAGE"~ 9,
word_enc =="BANJO"~	10,
word_enc =="BANKER"~	11,
word_enc =="BARLEY"~	12,
word_enc =="BARREL"~	13,
word_enc =="BASEBALL"~	14,
word_enc =="BEAKER"~	15,
word_enc =="BEAVER"~	16,
word_enc =="BEETLE"~	17,
word_enc =="BERRY"~	18,
word_enc =="BINDER"~	19,
word_enc =="BISCUIT"~	20,
word_enc =="BISON"~	21,
word_enc =="BLACKBOARD"~	22,
word_enc =="BLENDER"~	23,
word_enc =="BOTTLE"~	24,
word_enc =="BRACELET"~	25,
word_enc =="BRIEFCASE"~	26,
word_enc =="BUILDING"~	27,
word_enc =="BUTLER"~	28,
word_enc =="BUTTER"~	29,
word_enc =="BUTTON"~	30,
word_enc =="CABBAGE"~	31,
word_enc =="CACTUS"~	32,
word_enc =="CAMEL"~	33,
word_enc =="CANDY"~	34,
word_enc =="CANOE"~	35,
word_enc =="CANVAS"~	36,
word_enc =="CARPET"~	37,
word_enc =="CARROT"~	38,
word_enc =="CARTON"~	39,
word_enc =="CASTLE"~	40,
word_enc =="CATTLE"~	41,
word_enc =="CELLO"~	42,
word_enc =="CHECKERS"~	43,
word_enc =="CHEDDAR"~	44,
word_enc =="CHERRY"~	45,
word_enc =="CHICKEN"~	46,
word_enc =="CHIPMUNK"~	47,
word_enc =="CLOSET"~	48,
word_enc =="COFFEE"~	49,
word_enc =="COMPASS"~	50,
word_enc =="COOKBOOK"~	51,
word_enc =='COOKIE'~	52,
word_enc =="COOLER"~	53,
word_enc =="CORAL"~	54,
word_enc =="COTTAGE"~	55,
word_enc =="COTTON"~	56,
word_enc =="CRACKER"~	57,
word_enc =="CRAYON"~	58,
word_enc =="CRICKET"~	59,
word_enc =="CRYSTAL"~	60,
word_enc =="CURTAIN"~	61,
word_enc =="CUSHION"~	62,
word_enc =="DAISY"~	63,
word_enc =="DENIM"~	64,
word_enc =="DENTIST"~	65,
word_enc =="DESSERT"~	66,
word_enc =="DIAPER"~	67,
word_enc =="DINNER"~	68,
word_enc =="DOLLAR"~	69,
word_enc =="DOLPHIN"~	70,
word_enc =="DONKEY"~	71,
word_enc =="DOORBELL"~	72,
word_enc =="DOUGHNUT"~	73,
word_enc =="DRAWING"~	74,
word_enc =="DRESSER"~	75,
word_enc =="DRIVEWAY"~	76,
word_enc =="DUSTPAN"~	77,
word_enc =="EAGLE"~	78,
word_enc =="EARRING"~	79,
word_enc =="ENGINE"~	80,
word_enc =="ESSAY"~	81,
word_enc =="FAUCET"~	82,
word_enc =="FEATHER"~	83,
word_enc =="FLANNEL"~	84,
word_enc =="FLASHLIGHT"~	85,
word_enc =="FOLDER"~	86,
word_enc =="FOOTBALL"~	87,
word_enc =="FOREST"~	88,
word_enc =="FOSSIL"~	89,
word_enc =="FOUNTAIN"~	90,
word_enc =="FREEZER"~	91,
word_enc =="GARBAGE"~	92,
word_enc =="GARDEN"~	93,
word_enc =="GARLIC"~	94,
word_enc =="GIRAFFE"~	95,
word_enc =="GUITAR"~	96,
word_enc =="GYMNAST"~	97,
word_enc =="HAMMER"~	98,
word_enc =="HAMMOCK"~	99,
word_enc =="HAMPER"~	100,
word_enc =="HANDBAG"~	101,
word_enc =="HANGER"~	102,
word_enc =="HEADBAND"~	103,
word_enc =="HELMET"~	104,
word_enc =="HIGHWAY"~	105,
word_enc =="HIKER"~	106,
word_enc =="HONEY"~	107,
word_enc =="IRON"~	108,
word_enc =="JACKET"~	109,
word_enc =="JELLY"~	110,
word_enc =="JEWEL"~	111,
word_enc =="KETCHUP"~	112,
word_enc =="KETTLE"~	113,
word_enc =="KEYBOARD"~	114,
word_enc =="KITCHEN"~	115,
word_enc =="LADDER"~	116,
word_enc =="LAUNDRY"~	117,
word_enc =="LAVA"~	118,
word_enc =="LAWYER"~	119,
word_enc =="LEMON"~	120,
word_enc =="LEOPARD"~	121,
word_enc =="LETTER"~	122,
word_enc =="LETTUCE"~	123,
word_enc =="LINEN"~	124,
word_enc =="LION"~	125,
word_enc =="LIPSTICK"~	126,
word_enc =="LITTER"~	127,
word_enc =="LIZARD"~	128,
word_enc =="LUGGAGE"~	129,
word_enc =="LUMBER"~	130,
word_enc =="MACHINE"~	131,
word_enc =="MAILBOX"~	132,
word_enc =="MARBLE"~	133,
word_enc =="MATTRESS"~	134,
word_enc =="MIRROR"~	135,
word_enc =="MITTEN"~	136,
word_enc =="MONKEY"~	137,
word_enc =="MOUNTAIN"~	138,
word_enc =="MUFFIN"~	139,
word_enc =="MUSHROOM"~	140,
word_enc =="NAPKIN"~	141,
word_enc =="NECKLACE"~	142,
word_enc =="NEEDLE"~	143,
word_enc =="NICKEL"~	144,
word_enc =="NOVEL"~	145,
word_enc =="OATMEAL"~	146,
word_enc =="OLIVE"~	147,
word_enc =="OMELET"~	148,
word_enc =="ONION"~	149,
word_enc =="ORANGE"~	150,
word_enc =="ORCHID"~	151,
word_enc =="OTTER"~	152,
word_enc =="OUTFIT"~	153,
word_enc =="OVEN"~	154,
word_enc =="OWL"~	155,
word_enc =="OYSTER"~	156,
word_enc =="PACKAGE"~	157,
word_enc =="PADDLE"~	158,
word_enc =="PAINTING"~	159,
word_enc =="PANTHER"~	160,
word_enc =="PARSLEY"~	161,
word_enc =="PASTA"~	162,
word_enc =="PASTRY"~	163,
word_enc =="PEANUT"~	164,
word_enc =="PEBBLE"~	165,
word_enc =="PENCIL"~	166,
word_enc =="PENGUIN"~	167,
word_enc =="PENNY"~	168,
word_enc =="PEPPER"~	169,
word_enc =="PICKLE"~	170,
word_enc =="PICNIC"~	171,
word_enc =="PIGEON"~	172,
word_enc =="PILLOW"~	173,
word_enc =="PILOT"~	174,
word_enc =="PIZZA"~	175,
word_enc =="PLANET"~	176,
word_enc =="PLAYGROUND"~	177,
word_enc =="POPCORN"~	178,
word_enc =="POSSUM"~	179,
word_enc =="PRINTER"~	180,
word_enc =="PUDDING"~	181,
word_enc =="PUDDLE"~	182,
word_enc =="PUMPKIN"~	183,
word_enc =='PUZZLE'~	184,
word_enc =="RABBIT"~	185,
word_enc =="RACCOON"~	186,
word_enc =="RACKET"~	187,
word_enc =="RADISH"~	188,
word_enc =="RAILROAD"~	189,
word_enc =="RAISIN"~	190,
word_enc =="RATTLE"~	191,
word_enc =="RECEIPT"~	192,
word_enc =="RECORD"~	193,
word_enc =="REPORT"~	194,
word_enc =="RIBBON"~	195,
word_enc =="RIVER"~	196,
word_enc =="ROBOT"~	197,
word_enc =="RUNNER"~	198,
word_enc =="SADDLE"~	199,
word_enc =="SAILOR"~	200,
word_enc =="SALAD"~	201,
word_enc =="SALMON"~	202,
word_enc =="SANDWICH"~	203,
word_enc =="SEAFOOD"~	204,
word_enc =="SEASHORE"~	205,
word_enc =="SHAMPOO"~	206,
word_enc =="SHOELACE"~	207,
word_enc =="SHOVEL"~	208,
word_enc =="SHOWER"~	209,
word_enc =="SIDEWALK"~	210,
word_enc =="SNORKEL"~	211,
word_enc =="SODA"~	212,
word_enc =="SOFA"~	213,
word_enc =="SQUIRREL"~	214,
word_enc =="STATUE"~	215,
word_enc =="STICKER"~	216,
word_enc =="STOCKING"~	217,
word_enc =="SUGAR"~	218,
word_enc =="SUITCASE"~	219,
word_enc =="SUNRISE"~	220,
word_enc =="SWEATER"~	221,
word_enc =="TABLE"~	222,
word_enc =="TEACHER"~	223,
word_enc =="TOASTER"~	224,
word_enc =="TOOTHBRUSH"~	225,
word_enc =="TOURIST"~	226,
word_enc =="TOWEL"~	227,
word_enc =="TOWER"~	228,
word_enc =="TUBA"~	229,
word_enc =="TULIP"~	230,
word_enc =="TURNIP"~	231,
word_enc =="TURTLE"~	232,
word_enc =="VACUUM"~	233,
word_enc =="VALLEY"~	234,
word_enc =="VELVET"~	235,
word_enc =="WAGON"~	236,
word_enc =="WALNUT"~	237,
word_enc =="WALRUS"~	238,
word_enc =="WASHCLOTH"~	239,
word_enc =="ZIPPER"~	240))

sf11_total_encodingonly_new$blocknum_contin <- as.integer(sf11_total_encodingonly_new$blocknum_contin )
```




```{r}
#encoding task 

detach(package:plyr)


Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}


encoding_sf11_avg <- sf11_total_encodingonly_new %>% 
  group_by(image, word_enc) %>% 
  mutate(resp_mode = Mode(response)) %>%  #takes the mode of responses based on word and trial 
  mutate(similar_to_avg = case_when(response == resp_mode ~ 1, #when the response is the mode - 1
                               response != resp_mode ~ 0)) %>% #when response is not the mode - 0
  arrange(subject, blocknum) %>% #arranges it back by subject 
  group_by(subject, blocknum) %>% 
  mutate(sum_encoding_sim = sum(similar_to_avg)) #creates a sum by block 


encoding_sf11_avg_2 <- encoding_sf11_avg %>% 
  group_by(subject) %>% 
  mutate(similar_to_avg_percent = sum(similar_to_avg)/192*100) %>% 
  summarise(mean_enc = mean(similar_to_avg_percent, na.rm = TRUE))

#Calculate average encoding not based on trialcode, but based on actual stimuli on the screen (in column "image"). This is because of the way I coded it, the item in trialcode maps to multiple images. Therefore, Image is the column needed to determine which "task" the participants are performing on that trial 

#chance is 55.7% for 192 trials 

mean_encoding_11 <- mean(encoding_sf11_avg_2$mean_enc, na.rm = TRUE)
mean_encoding_11

```

```{r}
#create separate dataframes for between subjects manipulations
#between subjects manipulation here is same vs novel NOT high vs mid 

#removes switch from control also

sf11_total_encodingonly_between <- encoding_sf11_avg %>% 
  mutate(between_condition = case_when(blockcode == "control_mid_same" ~ "same",
                                         blockcode == "control_high_same" ~"same",
                                         blockcode == "high_control_same" ~"same",
                                         blockcode == "mid_control_same" ~"same",
                                       blockcode == "control_mid_novel" ~ "novel",
                                         blockcode == "control_high_novel" ~"novel",
                                         blockcode == "high_control_novel" ~"novel",
                                         blockcode == "mid_control_novel" ~"novel")) %>% 
  filter(task_switch == "switch" & condition == "high"|task_switch == "repeat" & condition == "high"|task_switch == "start" & condition == "high"| task_switch == "switch" & condition == "mid"| task_switch == "repeat" & condition == "mid"| task_switch == "start" & condition == "mid"|task_switch == "repeat" & condition == "cont_high"| task_switch == "start" & condition == "cont_high"| task_switch == "repeat" & condition == "cont_mid"| task_switch == "start" & condition == "cont_mid")



sf11_total_encodingonly_same <-sf11_total_encodingonly_between %>% 
  filter(between_condition == "same")


sf11_total_encodingonly_novel <-sf11_total_encodingonly_between %>% 
  filter(between_condition == "novel")
```



```{r}
#compare mean encoding performance between same and novel 

encoding_sf11_avg_3 <- sf11_total_encodingonly_between %>% 
  group_by(subject, between_condition) %>% 
  mutate(similar_to_avg_percent = sum(similar_to_avg)/192*100) %>% 
  summarise(mean_enc = mean(similar_to_avg_percent, na.rm = TRUE))

mean_encoding_11_2 <- mean(encoding_sf11_avg_3$mean_enc, na.rm = TRUE)
mean_encoding_11_2


encoding_sf11_avg_3_same <- encoding_sf11_avg_3 %>% 
  filter(between_condition == "same")

mean_encoding_11_same <- mean(encoding_sf11_avg_3_same$mean_enc, na.rm = TRUE)
mean_encoding_11_same


sd_same <-sd(encoding_sf11_avg_3_same$mean_enc, na.rm = TRUE)


se_same <- sd_same / sqrt(41)


encoding_sf11_avg_3_novel <- encoding_sf11_avg_3 %>% 
  filter(between_condition == "novel")

mean_encoding_11_novel <- mean(encoding_sf11_avg_3_novel$mean_enc, na.rm = TRUE)
mean_encoding_11_novel


sd_novel <-sd(encoding_sf11_avg_3_novel$mean_enc, na.rm = TRUE)


se_novel <- sd_novel / sqrt(43)



t.test(encoding_sf11_avg_3_same$mean_enc, encoding_sf11_avg_3_novel$mean_enc)

library(lsr)

cohensD(mean_enc ~ between_condition,data = encoding_sf11_avg_3)
```



So far, we found that accuracy during the encoding task did not not differ for repeated and novel context switches 



```{r}
#sets path to data
#changes ann files to txt files 
path_to_data <- "~/Documents/DuBrow_lab/Projects/Multitasking/switchfreq_11/Raw_Data"
setwd(path_to_data)
ann_files <- list.files(path_to_data, recursive = TRUE, pattern = "*.ann", full.names = TRUE)
text_files <- gsub(".ann", ".txt", ann_files)
text_files
file.rename(from= ann_files, to = text_files)
```




```{r}
library(plyr)

# Define the list of subject IDs explicitly
subjects <- c("137455", "138853", "139435", "142837", "145912", "146857", "148570", "149335", 
  "149395", "149437", "149512", "150661", "151762", "151921", "152983", "153382", 
  "154174", "154264", "154348", "154444", "154801", "154906", "154984", "155560", 
  "156130", "156385", "156418", "156436", "156541", "156544", "156550", "156586", 
  "156595", "156604", "156691", "156739", "156751", "156784", "156961", "156970", 
  "156979", "156988", "157000", "157027", "157057", "157063", "157069", "157159", 
  "157171", "157198", "157210", "157261", "157270", "157327", "157339", "157354", 
  "157381", "157411", "157432", "157435", "157438", "157447", "157456", "157471", 
  "157474", "157486", "157489", "157498", "157549", "157603", "157621", "157639", 
  "157648", "157663", "157696", "157837", "157912", "158350", "742243848", 
  "742243852", "742243854", "154438", "157246", "152818")

process_subject_data <- function(subject_id) {
  # Define the path to the subject's recall files
  recall_files <- dir_ls(paste0("~/Documents/DuBrow_lab/Projects/Multitasking/switchfreq_11/V1/Raw_data/", subject_id), glob = "*.txt")
  
  # Load the recall data
  recall_data <- ldply(recall_files, function(f) import(f, quote = ""))
  
  # Clean the .id column
  recall_data <- recall_data %>% 
    mutate(.id = str_replace_all(.id, "/Users/lrait/Documents/DuBrow_lab/Projects/Multitasking/switchfreq_11/V1/Raw_data/", ""))
  
  # Separate final recall data and other recall data
  final_recall <- recall_data %>% 
    filter(.id == paste0(subject_id, "/", "finalrecall.txt"))
  
  recall <- recall_data %>% 
    filter(!grepl(paste0(subject_id, "/", "finalrecall.txt"), .id))
  
  list(final_recall = final_recall, recall = recall)
}

# Process data for each subject and assign to individual variables
for (subject_id in subjects) {
  data <- process_subject_data(subject_id)
  
  assign(paste0("recall_data_final_", subject_id), data$final_recall)
  assign(paste0("recall_", subject_id), data$recall)
}
```


#IMMEDIATE RECALL 

```{r}
#most important code chunk.- immediate recall 
library(stringr)
detach(package:plyr) #MUST RUN THIS

split_enc_11 <- split(sf11_total_encodingonly_between,sf11_total_encodingonly_between$subject)

#list of all subjects individual recall data
recall11_df_immed = list(recall_137455,recall_138853, recall_139435, recall_142837, recall_145912, recall_146857, recall_148570, recall_149335, recall_149395, recall_149437, recall_149512, recall_150661, recall_151762, recall_151921, recall_152983, recall_153382, recall_154174, recall_154264, recall_154348, recall_154444, recall_154801, recall_154906, recall_154984, recall_155560, recall_156130, recall_156385, recall_156418, recall_156436, recall_156541, recall_156544, recall_156550, recall_156586, recall_156595, recall_156604, recall_156691, recall_156739, recall_156751, recall_156784, recall_156961, recall_156970, recall_156979, recall_156988, recall_157000, recall_157027, recall_157057, recall_157063, recall_157069, recall_157159, recall_157171, recall_157198, recall_157210, recall_157261, recall_157270, recall_157327, recall_157339, recall_157354,recall_157381, recall_157411, recall_157432, recall_157435, recall_157438, recall_157447, recall_157456, recall_157471, recall_157474, recall_157486, recall_157489, recall_157498, recall_157549, recall_157603, recall_157621, recall_157621, recall_157639, recall_157648, recall_157663, recall_157696, recall_157837, recall_157912, recall_158350, recall_742243848, recall_742243852, recall_742243854, recall_154438, recall_157246, recall_152818)


#list of task data 
sf11_by_sub <- list(split_enc_11$'137455',split_enc_11$'138853', split_enc_11$'139435', split_enc_11$'142837', split_enc_11$'145912', split_enc_11$'146857', split_enc_11$'148570', split_enc_11$'149335', split_enc_11$'149395', split_enc_11$'149437', split_enc_11$'149512', split_enc_11$'150661', split_enc_11$'151762', split_enc_11$'151921', split_enc_11$'152983', split_enc_11$'153382', split_enc_11$'154174', split_enc_11$'154264', split_enc_11$'154348', split_enc_11$'154444', split_enc_11$'154801', split_enc_11$'154906', split_enc_11$'154984', split_enc_11$'155560', split_enc_11$'156130', split_enc_11$'156385', split_enc_11$'156418', split_enc_11$'156436', split_enc_11$'156541', split_enc_11$'156544', split_enc_11$'156550', split_enc_11$'156586', split_enc_11$'156595', split_enc_11$'156604', split_enc_11$'156691', split_enc_11$'156739', split_enc_11$'156751', split_enc_11$'156784', split_enc_11$'156961', split_enc_11$'156970', split_enc_11$'156979', split_enc_11$'156988', split_enc_11$'157000', split_enc_11$'157027', split_enc_11$'157057', split_enc_11$'157063', split_enc_11$'157069', split_enc_11$'157159', split_enc_11$'157171', split_enc_11$'157198', split_enc_11$'157210', split_enc_11$'157261', split_enc_11$'157270', split_enc_11$'157327', split_enc_11$'157339', split_enc_11$'157354',split_enc_11$'157381', split_enc_11$'157411', split_enc_11$'157432', split_enc_11$'157435', split_enc_11$'157438', split_enc_11$'157447', split_enc_11$'157456', split_enc_11$'157471', split_enc_11$'157474', split_enc_11$'157486', split_enc_11$'157489', split_enc_11$'157498', split_enc_11$'157549', split_enc_11$'157603', split_enc_11$'157621', split_enc_11$'157621', split_enc_11$'157639', split_enc_11$'157648', split_enc_11$'157663', split_enc_11$'157696', split_enc_11$'157837', split_enc_11$'157912', split_enc_11$'158350', split_enc_11$'742243848', split_enc_11$'742243852', split_enc_11$'742243854', split_enc_11$`154438`, split_enc_11$`157246`, split_enc_11$`152818`)


#for every subject:
c = 0 
for (ssid in array(1:length(recall11_df_immed))){
    i = sf11_by_sub[[ssid]]
    j = recall11_df_immed[[ssid]]
    c = c +1 
    output  <- i %>% 
      mutate(recalls = tolower(word_enc) %in% tolower(j$V3))%>%  #matches the recall with task word
      mutate(recalls = case_when(recalls == "TRUE" ~ 1, #if recalled word, puts a 1 
                               recalls == "FALSE" ~ 0)) %>%  
      group_by(condition, trialcode) %>% 
      mutate(sum_recall = sum(recalls)) %>% # this column sums the recalls by condition and task
      group_by(blocknum) %>% 
      mutate(sum_recall_block = sum(recalls)) %>% #sums recalls by block
      group_by(trialcode) %>% 
      mutate(sum_recall_trialcode = sum(recalls)) #sums recalls just by task 
    if (c ==1) {
      sf11_total = output
    } else {
      sf11_total = rbind(sf11_total,output)
    }}

sf11_total
```





```{r}
#recall by task - immediate 
library(dplyr)

sf11_total_2_immed<- sf11_total %>% 
  group_by(subject) %>% 
  mutate(recall_percent2 = sum(recalls)/192*100) %>% 
  summarise(mean_rec = mean(recall_percent2, na.rm = TRUE))



#plot of each subjects recall in order 
sf11_total_2_immed %>% 
  ggplot(aes(x = reorder(as.character(subject), mean_rec), y = mean_rec))+
  geom_col(fill = "orchid", width = .8)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  labs(title    = "Percent of Total Words Recalled for Each Subject",
         x        = "Subject Number",
         y        = "Percent Recalled")


mean_recall11<- mean(sf11_total_2_immed$mean_rec, na.rm = TRUE)
mean_recall11


sd_11 <-sd(sf11_total_2_immed$mean_rec, na.rm = TRUE)
```


```{r}
#outliers at immed, all participants included 
sf11_total_2_immed %>% 
  arrange(mean_rec)


sd_11 <-sd(sf11_total_2_immed$mean_rec, na.rm = TRUE)

mean_recall11 <- mean(sf11_total_2_immed$mean_rec, na.rm = TRUE)

mean_recall11 + (2.5 * sd_11) 
mean_recall11 - (2.5 * sd_11)

```




```{r}
#mean recall between same and novel 

sf11_total_2_immed_between<- sf11_total %>% 
  group_by(subject, between_condition) %>% 
  mutate(recall_percent2 = sum(recalls)/192*100) %>% 
  summarise(mean_rec = mean(recall_percent2, na.rm = TRUE))

sf11_total_2_immed_between_same <- sf11_total_2_immed_between %>% 
  filter(between_condition == "same")


mean_recall11_same<- mean(sf11_total_2_immed_between_same$mean_rec, na.rm = TRUE)
mean_recall11_same


sf11_total_2_immed_between_novel <- sf11_total_2_immed_between %>% 
  filter(between_condition == "novel")

mean_recall11_novel<- mean(sf11_total_2_immed_between_novel$mean_rec, na.rm = TRUE)
mean_recall11_novel


t.test(sf11_total_2_immed_between_same$mean_rec, sf11_total_2_immed_between_novel$mean_rec)


cohensD(mean_rec~between_condition, sf11_total_2_immed_between)
```

Free-recall accuracy was greater for repeated versus novel switches suggesting that participants’ memory was better for words from lists containing repeated scenes.



```{r}
#separate by between condition 
sf11_total_2 <-sf11_total %>% 
  mutate(between_condition = case_when(blockcode == "control_mid_same" ~ "same",
                                         blockcode == "control_high_same" ~"same",
                                         blockcode == "high_control_same" ~"same",
                                         blockcode == "mid_control_same" ~"same",
                                       blockcode == "control_mid_novel" ~ "novel",
                                         blockcode == "control_high_novel" ~"novel",
                                         blockcode == "high_control_novel" ~"novel",
                                         blockcode == "mid_control_novel" ~"novel")) %>% 
  filter(task_switch == "switch" & condition == "high"|task_switch == "repeat" & condition == "high"|task_switch == "start" & condition == "high"| task_switch == "switch" & condition == "mid"| task_switch == "repeat" & condition == "mid"| task_switch == "start" & condition == "mid"|task_switch == "repeat" & condition == "cont_high"| task_switch == "start" & condition == "cont_high"| task_switch == "repeat" & condition == "cont_mid"| task_switch == "start" & condition == "cont_mid") %>% 
    mutate(condition_control = case_when(condition == "cont_mid" ~ "no switch",
                                         condition == "cont_high" ~"no switch",
                                         condition == "high" ~"switch",
                                         condition == "mid" ~"switch")) %>% 
  mutate(condition_mh = case_when(condition == "cont_mid" ~ "mid",
                                         condition == "cont_high" ~"high",
                                         condition == "high" ~"high",
                                         condition == "mid" ~"mid")) %>% 
     mutate(condition_high = case_when(condition == "cont_high" ~"cont_high",
                                         condition == "high" ~"high")) %>% 
  mutate(condition_low = case_when(condition == "cont_mid" ~ "cont_mid",
                                         condition == "mid" ~"mid")) 


sf11_total_same <- sf11_total_2 %>% 
  filter(between_condition == "same")


sf11_total_novel <- sf11_total_2 %>% 
  filter(between_condition == "novel")
```



```{r}

#plot average recalls for task and condition

#separate control into high and mid paired 
#no switch items in the control 

#difference score error bars same 


sf12_total_tally_same_immed <- sf11_total_same %>% 
  group_by(subject, condition) %>% 
  tally() 


sf12_total_same_2 <- sf11_total_same %>% 
  dplyr:: select(subject, condition, trialcode, sum_recall, recalls) %>% 
  group_by(subject, condition) %>% 
  mutate(sum_recall2 = sum(recalls)) %>% 
  summarise(mean_rec_cond = mean(sum_recall2)) 

merged_same <- merge(sf12_total_same_2,sf12_total_tally_same_immed)

merged_same <- merged_same %>% 
  mutate(prop_cond = mean_rec_cond/n)

difference_error_same <- merged_same %>% 
  dplyr::select(subject, condition, prop_cond) %>% 
  reshape(idvar = "subject", timevar = "condition", direction = "wide") %>% 
  group_by(subject) %>% 
  mutate(diff_cont_high = sum(prop_cond.high- prop_cond.cont_high)) %>% 
  mutate(diff_cont_mid = sum(prop_cond.mid- prop_cond.cont_mid))


difference_error_same2 <- difference_error_same %>% 
  plyr::summarise(avg_diff_cont_high = mean(diff_cont_high),
            avg_diff_cont_mid = mean(diff_cont_mid))


library(plotrix)


se_cont_high_same <- std.error(difference_error_same$diff_cont_high)

se_cont_mid_same <- std.error(difference_error_same$diff_cont_mid)


same_immediate_df = data.frame(condition = c("control (mid)", "mid", "control (high)", "high"), n = c(41,41,41,41), mean = c(0.2507953, 0.2642276, 0.2131495, 0.2500000), standerr = c(0.01539218, 0.01539218, 0.01614067, 0.01614067))

same_immediate_df<- same_immediate_df %>% 
  mutate(condition = fct_relevel(condition, "control (mid)", "mid", "control (high)", "high"))

same_immediate_df %>% 
  ggplot(aes(x = condition, y = mean)) +
  geom_col(width = .7, aes(fill = condition), alpha = .8, color = "black", linewidth = .3) +
  labs(title    = "Percentage of Recalls by Condition",
         x        = "Condition",
         y        = "Percent Recalled")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=mean-standerr, ymax=mean+standerr))+
scale_y_continuous(labels = scales::percent_format(accuracy = 1L), expand = c(0,0))+
  scale_x_discrete(labels=c("control" = "Control","mid"= "Low Switch", "high" = "High Switch"))+
    scale_fill_manual(values = c("lightgreen", "green4", "lavender", "darkorchid4"))


```

Interestingly, there was a boost in recall performance for high-switch, over no-switch, items
when switching back to repeated contexts.


```{r}
#model for the just same condition - used for paper 

model_condition_same_11_2<- glmer(recalls~condition_mh*condition_control +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_same)
summary(model_condition_same_11_2)



sf11_total_same<- sf11_total_same %>% 
  mutate(condition = fct_relevel(condition, "cont_high","high", "mid", "cont_mid"))

library(lme4)
model_condition_same_11_3<- glmer(recalls~condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_same)
summary(model_condition_same_11_3)

```

```{r}
library(r2glmm)
library(effectsize)

r2glmm::r2beta(model_condition_same_11_2, partial = TRUE)

r2glmm::r2beta(model_condition_same_11_3, partial = TRUE)

```




```{r}
#plot average recalls for task and condition

#separate control into high and mid paired 
#no switch items in the control 
#difference score error bars novel 


sf12_total_tally_novel_immed <- sf11_total_novel %>% 
  group_by(subject, condition) %>% 
  tally() 

sf12_total_novel_2 <- sf11_total_novel %>% 
  dplyr:: select(subject, condition, trialcode, sum_recall, recalls) %>% 
  group_by(subject, condition) %>% 
  mutate(sum_recall2 = sum(recalls)) %>% 
  summarise(mean_rec_cond = mean(sum_recall2)) 

merged_novel <- merge(sf12_total_novel_2,sf12_total_tally_novel_immed)


merged_novel <- merged_novel %>% 
  mutate(prop_cond = mean_rec_cond/n)



difference_error_novel <- merged_novel %>% 
  dplyr::select(subject, condition, prop_cond) %>% 
  reshape(idvar = "subject", timevar = "condition", direction = "wide") %>% 
  group_by(subject) %>% 
  mutate(diff_cont_high = sum(prop_cond.high- prop_cond.cont_high)) %>% 
  mutate(diff_cont_mid = sum(prop_cond.mid- prop_cond.cont_mid))




library(plotrix)


se_cont_high_novel <- std.error(difference_error_novel$diff_cont_high)

se_cont_mid_novel <- std.error(difference_error_novel$diff_cont_mid)


novel_immediate_df = data.frame(condition = c("control (mid)", "mid", "control (high)", "high"), n = c(43,43,43,43), mean = c(0.2103134, 0.2078488, 0.2275025, 0.1879845), standerr = c(0.01466818, 0.01466818, 0.0160976, 0.0160976))

novel_immediate_df<- novel_immediate_df %>% 
  mutate(condition = fct_relevel(condition, "control (mid)", "mid", "control (high)", "high"))

immed_within_nov <- novel_immediate_df %>% 
  ggplot(aes(x = condition, y = mean)) +
  geom_col(width = .7, aes(fill = condition), alpha = .8, color = "black", linewidth = .3) +
  labs(title    = "Percentage of Recalls by Condition",
         x        = "Condition",
         y        = "Percent Recalled")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=mean-standerr, ymax=mean+standerr))+
scale_y_continuous(labels = scales::percent_format(accuracy = 1L), expand = c(0,0))+
  scale_x_discrete(labels=c("control (mid)" = "Control (Low)","mid"= "Low Switch", "high" = "High Switch"))+
    scale_fill_manual(values = c("lightgreen", "green4", "lavender", "darkorchid4"))
```

With exposure to novel contexts, recall performance was reduced when switching contexts at a high rate, compared to not switching. There was no detriment to memory for low-switch, compared to no-switch, items with novel context switching. Performance is disrupted only when switching to novel contexts at a high rate.




```{r}
#model for the just novel condition - used for paper 

model_condition_novel_11_2<- glmer(recalls~condition_mh*condition_control +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_novel)
summary(model_condition_novel_11_2)

plot_model(model_condition_novel_11_2, type = "int")

r2glmm::r2beta(model_condition_novel_11_2, partial = TRUE)


sf11_total_novel<- sf11_total_novel %>% 
  mutate(condition = fct_relevel(condition, "high","cont_mid", "cont_high", "mid"))

sf11_total_novel_cond <- sf11_total_novel %>% 
  filter(condition == "cont_high" | condition =="high")

model_condition_novel_11_3<- glmer(recalls~condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_novel_cond)
summary(model_condition_novel_11_3)


r2glmm::r2beta(model_condition_novel_11_3, partial = TRUE)

```





```{r}

same_immediate_df <- same_immediate_df %>% 
  mutate(between_condition = "same")

novel_immediate_df <- novel_immediate_df %>% 
  mutate(between_condition = "novel")


between_condition_bind_immed_full2 <- rbind(same_immediate_df, novel_immediate_df)


between_condition_bind_immed_full2 %>% 
  ggplot(aes(x = condition, fill = interaction(between_condition,condition), y = mean)) +
  geom_bar(position="dodge", stat="identity", color = "black", linewidth = .3, alpha = .8) +
  labs(title    = "Percentage of Recalls by Condition and Task",
         x        = "Condition",
         y        = "Percent Recalled")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=mean-standerr, ymax=mean +standerr))+
  scale_y_continuous(labels = scales::percent, expand = c(0,0))+
  scale_x_discrete(labels=c("control (mid)" = "Control (Low)","mid"= "Low Switch", "control (high)" = "Control (High)", "high" = "High Switch"))+
  scale_fill_manual(name = "Condition", values=c("lightgreen", "lightgreen", "darkgreen", "darkgreen", "lavender", "lavender","darkorchid4", "darkorchid4")) +
  facet_wrap(.~between_condition)
```


There was a signifcant three-way interaction, highlighting that the relationship between switch rate (high vs. low) and switch type (no-switch vs. switch) differed depending on whether scenes were repeating or novel.



```{r}
#these models used for paper 

model_condition_total_11_2<- glmer(recalls~condition*between_condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_2)
summary(model_condition_total_11_2)


sf11_total_2_high <- sf11_total_2 %>% 
  filter(condition == "high" | condition == "cont_high")


model_condition_total_11_2_high<- glmer(recalls~condition*between_condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_2_high)
summary(model_condition_total_11_2_high)

r2glmm::r2beta(model_condition_total_11_2_high, partial = TRUE)



sf11_total_2<- sf11_total_2 %>% 
  mutate(condition_mh = fct_relevel(condition_mh, "mid","high"))





model_condition_total_11_3<- glmer(recalls~condition_mh*condition_control*between_condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_2)
summary(model_condition_total_11_3)


r2glmm::r2beta(model_condition_total_11_3, partial = TRUE)


model_condition_total_11_4<- glmer(recalls~between_condition*condition_mh +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_2)
summary(model_condition_total_11_4)

r2glmm::r2beta(model_condition_total_11_4, partial = TRUE)


```




```{r}
#model 2x2 mid/high and switch/repeat 

sf11_total_3<-sf11_total_2 %>% 
  filter(condition == "high" | condition == "mid") %>% 
  filter(task_switch == "switch" | task_switch == "repeat")



#same

sf11_total_same_transition<-sf11_total_3 %>% 
  filter(condition == "high" | condition == "mid") %>% 
  filter(task_switch == "switch" | task_switch == "repeat") %>% 
  filter(between_condition == "same")

model_transition_11_same<- glmer(recalls~condition*task_switch + list_half+(1|subject)+ (1|word_enc), family = binomial, data = sf11_total_same_transition)
summary(model_transition_11_same)


plot_model(model_transition_11_same, type = "int")

#novel 

sf11_total_nov_transition<-sf11_total_3 %>% 
  filter(condition == "high" | condition == "mid") %>% 
  filter(task_switch == "switch" | task_switch == "repeat") %>% 
  filter(between_condition == "novel")

model_transition_11_novel<- glmer(recalls~condition*task_switch +list_half + blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_nov_transition)
summary(model_transition_11_novel)


plot_model(model_transition_11_novel, type = "int")


#total

model_transition_11<- glmer(recalls~condition*task_switch*between_condition +list_half + blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_3)
summary(model_transition_11)


plot_model(model_transition_11, type = "int")


sf11_total_3_mid <- sf11_total_3 %>% 
  filter(condition == "high") %>% 
  filter(between_condition == "novel")


model_transition_11_mid<- glmer(recalls~task_switch +list_half + blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_3_mid)
summary(model_transition_11_mid)



```





```{r}
#boundary vs preboundary- supplementary materials 


sf11_total_mid_spc_3<- sf11_total_2 %>% 
  filter(condition == "mid") %>% 
  filter(trialnum == "5" | trialnum == "6" |trialnum == "8" |trialnum == "9" |trialnum == "10" |trialnum == "12"| trialnum == "13" |trialnum == "14"| trialnum == "16" |trialnum == "17" |trialnum == "18" |trialnum == "20") %>%
  mutate(trialnum_new = case_when(trialnum == "5" ~ "boundary",
                                  trialnum == "6" ~ "postboundary",
                               trialnum == "8" ~ "preboundary",
                               trialnum == "9" ~ "boundary",
                               trialnum == "10" ~ "postboundary",
                               trialnum == "12" ~ "preboundary",
                               trialnum == "13" ~ "boundary",
                               trialnum == "14" ~ "postboundary",
                               trialnum == "16" ~ "preboundary",
                               trialnum == "17" ~ "boundary",
                               trialnum == "18" ~ "postboundary",
                               trialnum == "20" ~ "preboundary")) 



spc_mid_11_tally_immed2 <- sf11_total_mid_spc_3 %>% 
  group_by(subject, trialnum_new) %>% 
  tally() 



spc_mid_11_immed2 <- sf11_total_mid_spc_3 %>% 
  dplyr:: select(subject, trialnum_new, between_condition, recalls) %>% 
  group_by(subject, trialnum_new, between_condition) %>% 
  mutate(sum_recall2 = sum(recalls)) %>% 
  summarise(mean_rec_cond = mean(sum_recall2)) 


merged_spc_immed <- merge(spc_mid_11_immed2,spc_mid_11_tally_immed2)


merged_spc_immed <- merged_spc_immed %>% 
  mutate(prop_cond = mean_rec_cond/n)


merged_spc_immed<- merged_spc_immed %>% 
  mutate(trialnum_new = fct_relevel(trialnum_new, "preboundary", "boundary", "postboundary"))


library(Rmisc)

spc_mid_11_immed <- summarySEwithin(merged_spc_immed, measurevar="prop_cond", withinvars = c("trialnum_new", "between_condition"),idvar = "subject", na.rm=FALSE, conf.interval=.95)


spc_mid_11_immed %>% 
  ggplot(aes(x = trialnum_new, fill = interaction(between_condition,trialnum_new), y = prop_cond)) +
  geom_bar(position="dodge", stat="identity", color = "black", linewidth = .3, alpha = .8) +
  labs(title    = "Percentage of Recalls by Condition and Task",
         x        = "Transition Type",
         y        = "Percent Recalled")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=prop_cond-se, ymax=prop_cond+se))+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L), expand = c(0,0))+
  scale_fill_manual(name = "Transition Type", values=c("grey90", "grey90", "grey60", "grey60", "grey20", "grey20")) +
  facet_wrap(.~between_condition)

```


```{r}
#models for boundary vs preboundary 
detach(package:Rmisc) 
detach(package:plyr) #MUST RUN THIS

sf11_total_mid_spc_3<- sf11_total_mid_spc_3 %>% 
  mutate(trialnum_new = fct_relevel(trialnum_new, "boundary", "preboundary", "postboundary"))


sf11_total_mid_spc_4 <- sf11_total_mid_spc_3 %>% 
  filter(between_condition == "same")


sf11_total_mid_spc_3_model_total<- glmer(recalls~trialnum_new+ blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_mid_spc_4)
summary(sf11_total_mid_spc_3_model_total)

#confint(sf11_total_mid_spc_3_model_total)

```




```{r}
#prepare the data for temporal clustering by adding necessary columns to the recall dataframe 

add_columns <- function(recall_df, enc_df) {
  selected_enc_df <- enc_df[, c("condition", "trialcode", "subject", "blocknum", "list_half", "task_switch","trialnum", "blockcode", "word_enc")]
  merged_df <- left_join(recall_df, selected_enc_df, by = c("V3" = "word_enc"))
  return(merged_df)
}

# Apply the function for each pair of recall and encoding data frames
merged_recall_list <- Map(add_columns, recall11_df_immed, sf11_by_sub)


# Identify the common columns across all data frames
common_columns <- Reduce(intersect, lapply(merged_recall_list, colnames))

# Ensure that each data frame in the list contains only the common columns
cleaned_recall_list <- lapply(merged_recall_list, function(df) df[, common_columns])

# Combine the cleaned data frames
recall11_df_immed2 <- do.call("rbind", cleaned_recall_list)

```


```{r}
#set up for temporal clustering for MATLAB 
#encoding and retrieval for just blocks with mid in it 
#Same

sf11_midblocks_same <- sf11_total_encodingonly_new %>% 
  filter(blockcode == "control_mid_same" | blockcode == "mid_control_same")


sf10_mid_same <- split(sf11_midblocks_same,sf11_midblocks_same$subject)


encod_list_mid_same = list()
for (i in sf10_mid_same){
  encod_vert<- unstack(i, pool_number~blocknum)
  nrow <- max(sapply(encod_vert, length))
  encod_vert <- sapply(encod_vert, function(x) {
  length(x) <- 24
  x }) 
  encod_hor <- t(encod_vert) #transposes it 
  encod_list_mid_same[[length(encod_list_mid_same)+1]] = encod_hor}


names(encod_list_mid_same)  <- paste("mid_enc_same_", c(137455 ,138853 ,139435 ,142837 ,146857 ,149335 ,149395 ,149437 ,150661 ,151921 ,152983 ,154801 ,156385 ,156541 ,156595 ,156691 ,156739 ,156751 ,156961 ,156979 ,157027 ,157057 ,157063 ,157069 ,157159 ,157171 ,157261 ,157327 ,157339 ,157381 ,157411 ,157435 ,157447 ,157471,157489, 157549, 157603, 157621, 157639, 157663, 157837), sep="")




library(MASS)

encode_list_same <- do.call(rbind, encod_list_mid_same)

write.matrix(encode_list_same, file="encode_list11_mid_same.csv")


#######################
#recall for mid, same 

recall11_df_immed2_mid_same <- recall11_df_immed2 %>% 
  filter(blockcode == "control_mid_same" | blockcode == "mid_control_same")
  

split_rec_mid11_same <- split(recall11_df_immed2_mid_same,recall11_df_immed2_mid_same$subject)



recall_list_mid_same = list()
for (i in split_rec_mid11_same){
  recall_vert<- unstack(i, V2~blocknum)
  recall_vert <- sapply(recall_vert, function(x) {
  length(x) <- 24
  x }) 
  recall_hor <- t(recall_vert) #transposes it 
  recall_hor[is.na(recall_hor)] <- 0
  recall_list_mid_same[[length(recall_list_mid_same)+1]] = recall_hor}




names(recall_list_mid_same)  <- paste("mid_rec_",  c(137455 ,138853 ,139435 ,142837 ,146857 ,149335 ,149395 ,149437 ,150661 ,151921 ,152983 ,154801 ,156385 ,156541 ,156595 ,156691 ,156739 ,156751 ,156961 ,156979 ,157027 ,157057 ,157063 ,157069 ,157159 ,157171 ,157261 ,157327 ,157339 ,157381 ,157411 ,157435 ,157447 ,157471,157489, 157549, 157603, 157621, 157639, 157663, 157837), sep="")
recall_list_mid_same <- noquote(recall_list_mid_same)




recall_list <- do.call(rbind, recall_list_mid_same)




library(MASS)

write.matrix(recall_list, file="recall_list_11_mid_same2.csv")
```



```{r}
#temporal clustering for mid block 
temp_clustering_mid_same <- c(0.6294,
    0.7248,
    0.6681,
    0.5629,
    0.5605,
    0.6591,
    0.6255,
    0.5138,
    0.6104,
    0.6461,
    0.5482,
    0.6185,
    0.5719,
    0.6613,
    0.5038,
    0.6138,
    0.4907,
    0.5577,
    0.5731,
    0.6366,
    0.6410,
    0.5782,
    0.6771,
    0.5283,
    0.4851,
    0.6201,
    0.5966,
    0.5560,
    0.7666,
    0.5604,
    0.5135,
    0.7081,
    0.6737,
    0.5219,
    0.6758,
    0.6701,
    0.5893,
    0.6938,
    0.5371,
    0.4529,
    0.5647)

mean(temp_clustering_mid_same, na.rm = TRUE)
sd(temp_clustering_mid_same, na.rm = TRUE)/ sqrt(length(temp_clustering_mid_same))
```


```{r}
#set up for temporal clustering for MATLAB 
#encoding and retrieval for just blocks with high in it 
#Same

sf11_highblocks_same <- sf11_total_encodingonly_new %>% 
  filter(blockcode == "control_high_same" | blockcode == "high_control_same")


sf10_high_same <- split(sf11_highblocks_same,sf11_highblocks_same$subject)


encod_list_high_same = list()
for (i in sf10_high_same){
  encod_vert<- unstack(i, pool_number~blocknum)
  nrow <- max(sapply(encod_vert, length))
  encod_vert <- sapply(encod_vert, function(x) {
  length(x) <- 24
  x }) 
  encod_hor <- t(encod_vert) #transposes it 
  encod_list_high_same[[length(encod_list_high_same)+1]] = encod_hor}


names(encod_list_high_same)  <- paste("high_enc_same_", c(137455 ,138853 ,139435 ,142837 ,146857 ,149335 ,149395 ,149437 ,150661 ,151921 ,152983 ,154801 ,156385 ,156541 ,156595 ,156691 ,156739 ,156751 ,156961 ,156979 ,157027 ,157057 ,157063 ,157069 ,157159 ,157171 ,157261 ,157327 ,157339 ,157381 ,157411 ,157435 ,157447 ,157471,157489, 157549, 157603, 157621, 157639, 157663, 157837), sep="")



library(MASS)

encode_list_same <- do.call(rbind, encod_list_high_same)

write.matrix(encode_list_same, file="encode_list11_high_same.csv")


#######################
#recall for high, same 

recall11_df_immed2_high_same <- recall11_df_immed2 %>% 
  filter(blockcode == "control_high_same" | blockcode == "high_control_same")
  

split_rec_high11_same <- split(recall11_df_immed2_high_same,recall11_df_immed2_high_same$subject)



recall_list_high_same = list()
for (i in split_rec_high11_same){
  recall_vert<- unstack(i, V2~blocknum)
  recall_vert <- sapply(recall_vert, function(x) {
  length(x) <- 24
  x }) 
  recall_hor <- t(recall_vert) #transposes it 
  recall_hor[is.na(recall_hor)] <- 0
  recall_list_high_same[[length(recall_list_high_same)+1]] = recall_hor}




names(recall_list_high_same)  <- paste("high_rec_",  c(137455 ,138853 ,139435 ,142837 ,146857 ,149335 ,149395 ,149437 ,150661 ,151921 ,152983 ,154801 ,156385 ,156541 ,156595 ,156691 ,156739 ,156751 ,156961 ,156979 ,157027 ,157057 ,157063 ,157069 ,157159 ,157171 ,157261 ,157327 ,157339 ,157381 ,157411 ,157435 ,157447 ,157471,157489, 157549, 157603, 157621, 157639, 157663, 157837), sep="")
recall_list_high_same <- noquote(recall_list_high_same)




recall_list <- do.call(rbind, recall_list_high_same)




library(MASS)

write.matrix(recall_list, file="recall_list_11_high_same2.csv")
```


```{r}
temp_clustering_high_same <- c(
    0.5913,
    0.5412,
    0.5424,
    0.5107,
    0.6055,
    0.4648,
    0.6156,
    0.6725,
    0.5659,
    0.5806,
    0.5839,
    0.6848,
    0.5282,
       NaN,
    0.5872,
    0.6386,
    0.6223,
    0.4080,
    0.5349,
    0.5391,
    0.5076,
    0.5799,
    0.6160,
    0.6603,
    0.4538,
    0.7401,
    0.5735,
    0.4770,
    0.4298,
    0.5097,
    0.5944,
    0.8118,
    0.5348,
    0.5236,
    0.4721,
    0.6364,
    0.5932,
    0.6683,
    0.5731,
    0.6140,
    0.5145)

mean(temp_clustering_high_same, na.rm = TRUE)
sd(temp_clustering_high_same, na.rm = TRUE)/ sqrt(length(temp_clustering_high_same))

```



```{r}
temp_clustering_same_v1 <- c(0.6294,
    0.7248,
    0.6681,
    0.5629,
    0.5605,
    0.6591,
    0.6255,
    0.5138,
    0.6104,
    0.6461,
    0.5482,
    0.6185,
    0.5719,
    0.6613,
    0.5038,
    0.6138,
    0.4907,
    0.5577,
    0.5731,
    0.6366,
    0.6410,
    0.5782,
    0.6771,
    0.5283,
    0.4851,
    0.6201,
    0.5966,
    0.5560,
    0.7666,
    0.5604,
    0.5135,
    0.7081,
    0.6737,
    0.5219,
    0.6758,
    0.6701,
    0.5893,
    0.6938,
    0.5371,
    0.4529,
    0.5647,
    0.5913,
    0.5412,
    0.5424,
    0.5107,
    0.6055,
    0.4648,
    0.6156,
    0.6725,
    0.5659,
    0.5806,
    0.5839,
    0.6848,
    0.5282,
       NaN,
    0.5872,
    0.6386,
    0.6223,
    0.4080,
    0.5349,
    0.5391,
    0.5076,
    0.5799,
    0.6160,
    0.6603,
    0.4538,
    0.7401,
    0.5735,
    0.4770,
    0.4298,
    0.5097,
    0.5944,
    0.8118,
    0.5348,
    0.5236,
    0.4721,
    0.6364,
    0.5932,
    0.6683,
    0.5731,
    0.6140,
    0.5145)


mean(temp_clustering_same_v1, na.rm = TRUE)
sd(temp_clustering_same_v1, na.rm = TRUE)/ sqrt(length(temp_clustering_same_v1))
```



```{r}
#set up for temporal clustering for MATLAB 
#encoding and retrieval for just blocks with mid in it 
#novel

sf11_midblocks_novel <- sf11_total_encodingonly_new %>% 
  filter(blockcode == "control_mid_novel" | blockcode == "mid_control_novel")


sf10_mid_novel <- split(sf11_midblocks_novel,sf11_midblocks_novel$subject)


encod_list_mid_novel = list()
for (i in sf10_mid_novel){
  encod_vert<- unstack(i, pool_number~blocknum)
  nrow <- max(sapply(encod_vert, length))
  encod_vert <- sapply(encod_vert, function(x) {
  length(x) <- 24
  x }) 
  encod_hor <- t(encod_vert) #transposes it 
  encod_list_mid_novel[[length(encod_list_mid_novel)+1]] = encod_hor}


names(encod_list_mid_novel)  <- paste("mid_enc_novel_", c( 145912 ,148570, 149512, 151762,152818 ,153382 ,154174 ,154264 ,154348 ,154438 ,154444 ,154906 ,154984 ,155560 ,156130 ,156418 ,156436 ,156544 ,156550 ,156586 ,156604 ,156784 ,156970 ,156988 ,157000 ,157198 ,157210,157246 ,157270 ,157354 ,157432 ,157438 ,157456 ,157474 ,157486 ,157498 ,157648 ,157696 ,157912 ,158350 ,742243848 ,742243852 ,742243854), sep="")




library(MASS)

encode_list_novel <- do.call(rbind, encod_list_mid_novel)

write.matrix(encode_list_novel, file="encode_list11_mid_novel2.csv")


#######################
#recall for mid, novel 

recall11_df_immed2_mid_novel <- recall11_df_immed2 %>% 
  filter(blockcode == "control_mid_novel" | blockcode == "mid_control_novel")
  

split_rec_mid11_novel <- split(recall11_df_immed2_mid_novel,recall11_df_immed2_mid_novel$subject)



recall_list_mid_novel = list()
for (i in split_rec_mid11_novel){
  recall_vert<- unstack(i, V2~blocknum)
  recall_vert <- sapply(recall_vert, function(x) {
  length(x) <- 24
  x }) 
  recall_hor <- t(recall_vert) #transposes it 
  recall_hor[is.na(recall_hor)] <- 0
  recall_list_mid_novel[[length(recall_list_mid_novel)+1]] = recall_hor}




names(recall_list_mid_novel)  <- paste("mid_rec_",  c( 145912 ,148570, 149512, 151762,152818 ,153382 ,154174 ,154264 ,154348 ,154438 ,154444 ,154906 ,154984 ,155560 ,156130 ,156418 ,156436 ,156544 ,156550 ,156586 ,156604 ,156784 ,156970 ,156988 ,157000 ,157198 ,157210,157246 ,157270 ,157354 ,157432 ,157438 ,157456 ,157474 ,157486 ,157498 ,157648 ,157696 ,157912 ,158350 ,742243848 ,742243852 ,742243854), sep="")
recall_list_mid_novel <- noquote(recall_list_mid_novel)


recall_list <- do.call(rbind, recall_list_mid_novel)




library(MASS)

write.matrix(recall_list, file="recall_list_11_mid_novel3.csv")
```

```{r}
temp_clustering_mid_novel <- c( 0.5586,
    0.7019,
    0.8088,
    0.9773,
    0.6331,
    0.6501,
    0.7295,
    0.6630,
    0.5439,
    0.6396,
    0.7151,
    0.7514,
    0.5306,
    0.7012,
    0.8864,
    0.6320,
    0.6272,
    0.5975,
    0.6163,
    0.6034,
    0.7672,
    0.5739,
    0.4773,
    0.7610,
    0.6844,
    0.5185,
    0.6524,
    0.6253,
    0.6223,
    0.5211,
    0.5104,
    0.5902,
    0.7207,
    0.5080,
    0.6682,
    0.6447,
    0.5158,
    0.5585,
    0.6618,
    0.6323,
    0.6088,
    0.4299,
    0.6889)


mean(temp_clustering_mid_novel, na.rm = TRUE)
sd(temp_clustering_mid_novel, na.rm = TRUE)/ sqrt(length(temp_clustering_mid_novel))
```

```{r}
#set up for temporal clustering for MATLAB 
#encoding and retrieval for just blocks with high in it 
#novel

sf11_highblocks_novel <- sf11_total_encodingonly_new %>% 
  filter(blockcode == "control_high_novel" | blockcode == "high_control_novel")


sf10_high_novel <- split(sf11_highblocks_novel,sf11_highblocks_novel$subject)


encod_list_high_novel = list()
for (i in sf10_high_novel){
  encod_vert<- unstack(i, pool_number~blocknum)
  nrow <- max(sapply(encod_vert, length))
  encod_vert <- sapply(encod_vert, function(x) {
  length(x) <- 24
  x }) 
  encod_hor <- t(encod_vert) #transposes it 
  encod_list_high_novel[[length(encod_list_high_novel)+1]] = encod_hor}


names(encod_list_high_novel)  <- paste("high_enc_novel_", c( 145912 ,148570, 149512, 151762,152818 ,153382 ,154174 ,154264 ,154348 ,154438 ,154444 ,154906 ,154984 ,155560 ,156130 ,156418 ,156436 ,156544 ,156550 ,156586 ,156604 ,156784 ,156970 ,156988 ,157000 ,157198 ,157210,157246 ,157270 ,157354 ,157432 ,157438 ,157456 ,157474 ,157486 ,157498 ,157648 ,157696 ,157912 ,158350 ,742243848 ,742243852 ,742243854), sep="")





library(MASS)

encode_list_novel <- do.call(rbind, encod_list_high_novel)

write.matrix(encode_list_novel, file="encode_list11_high_novel_2.csv")


#######################
#recall for high, novel 

recall11_df_immed2_high_novel <- recall11_df_immed2 %>% 
  filter(blockcode == "control_high_novel" | blockcode == "high_control_novel")
  

split_rec_high11_novel <- split(recall11_df_immed2_high_novel,recall11_df_immed2_high_novel$subject)



recall_list_high_novel = list()
for (i in split_rec_high11_novel){
  recall_vert<- unstack(i, V2~blocknum)
  recall_vert <- sapply(recall_vert, function(x) {
  length(x) <- 24
  x }) 
  recall_hor <- t(recall_vert) #transposes it 
  recall_hor[is.na(recall_hor)] <- 0
  recall_list_high_novel[[length(recall_list_high_novel)+1]] = recall_hor}




names(recall_list_high_novel)  <- paste("high_rec_",  c(145912 ,148570, 149512, 151762,152818 ,153382 ,154174 ,154264 ,154348 ,154438 ,154444 ,154906 ,154984 ,155560 ,156130 ,156418 ,156436 ,156544 ,156550 ,156604 ,156784 ,156970 ,156988 ,157000 ,157198 ,157210,157246 ,157270 ,157354 ,157432 ,157438 ,157456 ,157474 ,157486 ,157498 ,157648 ,157696 ,157912 ,158350 ,742243848 ,742243852 ,742243854), sep="")
recall_list_high_novel <- noquote(recall_list_high_novel)


recall_list <- do.call(rbind, recall_list_high_novel)


library(MASS)

write.matrix(recall_list, file="recall_list_11_high_novel_2.csv")
```

```{r}
temp_clustering_high_novel <- c(0.6218,
    0.7580,
    0.5822,
    0.6135,
    0.6605,
    0.6508,
    0.6780,
    0.6798,
    0.7765,
    0.6772,
    0.6140,
    0.6477,
    0.7175,
    0.6614,
    0.8262,
    0.6946,
    0.7339,
    0.4915,
    0.6327,
       NaN,
    0.7997,
    0.7396,
    0.7655,
    0.7857,
    0.6811,
    0.5203,
    0.6447,
    0.6798,
    0.7461,
    0.5364,
    0.7273,
    0.7668,
    0.5689,
    0.6760,
    0.7706,
    0.7299,
    0.5301,
    0.6069,
    0.7443,
    0.5735,
    0.4268,
    0.6687,
    0.8033)

mean(temp_clustering_high_novel, na.rm = TRUE)
sd(temp_clustering_high_novel, na.rm = TRUE)/ sqrt(length(temp_clustering_high_novel))
```


```{r}
temp_clustering_novel_v1 <- c( 0.5586,
    0.7019,
    0.8088,
    0.9773,
    0.6331,
    0.6501,
    0.7295,
    0.6630,
    0.5439,
    0.6396,
    0.7151,
    0.7514,
    0.5306,
    0.7012,
    0.8864,
    0.6320,
    0.6272,
    0.5975,
    0.6163,
    0.6034,
    0.7672,
    0.5739,
    0.4773,
    0.7610,
    0.6844,
    0.5185,
    0.6524,
    0.6253,
    0.6223,
    0.5211,
    0.5104,
    0.5902,
    0.7207,
    0.5080,
    0.6682,
    0.6447,
    0.5158,
    0.5585,
    0.6618,
    0.6323,
    0.6088,
    0.4299,
    0.6889,
    0.6218,
    0.7580,
    0.5822,
    0.6135,
    0.6605,
    0.6508,
    0.6780,
    0.6798,
    0.7765,
    0.6772,
    0.6140,
    0.6477,
    0.7175,
    0.6614,
    0.8262,
    0.6946,
    0.7339,
    0.4915,
    0.6327,
       NaN,
    0.7997,
    0.7396,
    0.7655,
    0.7857,
    0.6811,
    0.5203,
    0.6447,
    0.6798,
    0.7461,
    0.5364,
    0.7273,
    0.7668,
    0.5689,
    0.6760,
    0.7706,
    0.7299,
    0.5301,
    0.6069,
    0.7443,
    0.5735,
    0.4268,
    0.6687,
    0.8033)
    

mean(temp_clustering_novel_v1, na.rm = TRUE)
sd(temp_clustering_novel_v1, na.rm = TRUE)/ sqrt(length(temp_clustering_novel_v1))

length(temp_clustering_novel_v1)
```


```{r}
#greater than chance-level clust 

t.test(temp_clustering_high_novel, mu = .5)

t.test(temp_clustering_high_same, mu = .5)

t.test(temp_clustering_mid_novel, mu = .5)

t.test(temp_clustering_mid_same, mu = .5)
```



```{r}
#compare 

t.test(temp_clustering_high_novel, temp_clustering_high_same)
#participants recalled more items in order during the high condition in the novel condition than in the high condition in the switch back condition 


t.test(temp_clustering_mid_novel, temp_clustering_mid_same)
#participants recalled more items in order during the mid condition in the novel condition than in the mid condition in the switch back condition 


t.test(temp_clustering_high_same, temp_clustering_mid_same)


t.test(temp_clustering_mid_novel, temp_clustering_high_novel)


t.test(temp_clustering_novel_v1, temp_clustering_same_v1)


cd_df_novel <- data.frame(between_condition = rep("novel",times = 86),
                    temp_score = temp_clustering_novel_v1)


cd_df_same <- data.frame(between_condition = rep("same",times = 82),
                    temp_score = temp_clustering_same_v1)


cd_df_both<- rbind(cd_df_same, cd_df_novel)

cohensD(temp_score~between_condition, cd_df_both)

```


Both switch rates across both levels of familiarity showed significant binding of items to their temporal context, as measured by greater than chance-level temporal clustering. However, when individuals were switching to novel versus repeated contexts, there was a greater reliance on temporal information (i.e., higher temporal clustering)



```{r}
#plot temporal clustering 
#difference score error bars novel 

temp_clust_11v1 <- import("temp_clustering_sf11_v1.csv")



temp_clust_11v1_2 <- temp_clust_11v1 %>% 
  group_by(condition, between_condition, subject) %>% 
  summarise(mean_temp_clust = mean(temp_clust_score)) 

difference_error_temp_clust <- temp_clust_11v1 %>% 
  unite(condition2, condition:between_condition, remove = FALSE) %>% 
  dplyr::select(subject, condition2, temp_clust_score) %>% 
  reshape(idvar = "subject", timevar = "condition2", direction = "wide") %>% 
  group_by(subject) %>% 
  mutate(diff_same = sum(temp_clust_score.low_same- temp_clust_score.high_same)) %>% 
  mutate(diff_novel = sum(temp_clust_score.low_novel- temp_clust_score.high_novel))



se_cont_temp_same <- std.error(difference_error_temp_clust$diff_same)

se_cont_temp_nov <- std.error(difference_error_temp_clust$diff_novel)


temp_clust_within_df = data.frame(condition = c("low", "high","low","high"),between_condition = c("same", "same", "novel", "novel"), mean = c(0.6053634, 0.5725350, 0.6397326, 0.6728310), standerr = c(0.02040952, 0.02040952, 0.0200526, 0.0200526))

temp_clust_within_df<- temp_clust_within_df %>% 
  mutate(condition = fct_relevel(condition, "low", "high" ))

temp_clust_within_df %>% 
  ggplot(aes(x = condition, fill = interaction(between_condition,condition), y = mean)) +
  geom_bar(position="dodge", stat="identity", color = "black", linewidth = .3, alpha = .8) +
  labs(title    = "Temporal Clustering",
         x        = "Condition",
         y        = "Temporal Clustering Score")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=mean-standerr, ymax=mean+standerr))+
  scale_y_continuous(expand = c(0,0))+
  scale_x_discrete(labels=c("cont_mid" = "Control (Low)","mid"= "Low Switch", "cont_high" = "Control (High)", "high" = "High Switch"))+
  scale_fill_manual(name = "Condition", values=c("grey60", "grey20", "darkseagreen2", "darkgreen", "grey60", "grey20","lavender", "darkorchid4")) +
  facet_wrap(.~between_condition)+
  coord_cartesian(ylim = c(.5, .7))



```



```{r}

#model 
model_temp_cluster<- lmer(temp_clust_score~condition*between_condition+ (1|subject),  data = temp_clust_11v1)
summary(model_temp_cluster)

plot_model(model_temp_cluster, type = "int")
```


#FINAL RECALL


```{r}
#most important code chunk

split_enc_11 <- split(sf11_total_encodingonly_between,sf11_total_encodingonly_between$subject)

#list of all subjects individual recall data
recall11_df = list(recall_data_final_137455,recall_data_final_138853, recall_data_final_139435, recall_data_final_142837, recall_data_final_145912, recall_data_final_146857, recall_data_final_148570, recall_data_final_149335, recall_data_final_149395, recall_data_final_149437, recall_data_final_149512, recall_data_final_150661, recall_data_final_151762, recall_data_final_151921, recall_data_final_152983, recall_data_final_153382, recall_data_final_154174, recall_data_final_154264, recall_data_final_154348, recall_data_final_154444, recall_data_final_154801, recall_data_final_154906, recall_data_final_154984, recall_data_final_155560, recall_data_final_156130, recall_data_final_156385, recall_data_final_156418, recall_data_final_156436, recall_data_final_156541, recall_data_final_156544, recall_data_final_156550, recall_data_final_156586, recall_data_final_156595, recall_data_final_156604, recall_data_final_156691, recall_data_final_156739, recall_data_final_156751, recall_data_final_156784, recall_data_final_156961, recall_data_final_156970, recall_data_final_156979, recall_data_final_156988, recall_data_final_157000, recall_data_final_157027, recall_data_final_157057, recall_data_final_157063, recall_data_final_157069, recall_data_final_157159, recall_data_final_157171, recall_data_final_157198, recall_data_final_157210, recall_data_final_157261, recall_data_final_157270, recall_data_final_157327, recall_data_final_157339, recall_data_final_157354,recall_data_final_157381, recall_data_final_157411, recall_data_final_157432, recall_data_final_157435, recall_data_final_157438, recall_data_final_157447, recall_data_final_157456, recall_data_final_157471, recall_data_final_157474, recall_data_final_157486, recall_data_final_157489, recall_data_final_157498, recall_data_final_157549, recall_data_final_157603, recall_data_final_157621, recall_data_final_157621, recall_data_final_157639, recall_data_final_157648, recall_data_final_157663, recall_data_final_157696, recall_data_final_157837, recall_data_final_157912, recall_data_final_158350, recall_data_final_742243848, recall_data_final_742243852, recall_data_final_742243854, recall_data_final_154438, recall_data_final_157246, recall_data_final_152818)



#list of task data 
sf11_by_sub <- list(split_enc_11$'137455',split_enc_11$'138853', split_enc_11$'139435', split_enc_11$'142837', split_enc_11$'145912', split_enc_11$'146857', split_enc_11$'148570', split_enc_11$'149335', split_enc_11$'149395', split_enc_11$'149437', split_enc_11$'149512', split_enc_11$'150661', split_enc_11$'151762', split_enc_11$'151921', split_enc_11$'152983', split_enc_11$'153382', split_enc_11$'154174', split_enc_11$'154264', split_enc_11$'154348', split_enc_11$'154444', split_enc_11$'154801', split_enc_11$'154906', split_enc_11$'154984', split_enc_11$'155560', split_enc_11$'156130', split_enc_11$'156385', split_enc_11$'156418', split_enc_11$'156436', split_enc_11$'156541', split_enc_11$'156544', split_enc_11$'156550', split_enc_11$'156586', split_enc_11$'156595', split_enc_11$'156604', split_enc_11$'156691', split_enc_11$'156739', split_enc_11$'156751', split_enc_11$'156784', split_enc_11$'156961', split_enc_11$'156970', split_enc_11$'156979', split_enc_11$'156988', split_enc_11$'157000', split_enc_11$'157027', split_enc_11$'157057', split_enc_11$'157063', split_enc_11$'157069', split_enc_11$'157159', split_enc_11$'157171', split_enc_11$'157198', split_enc_11$'157210', split_enc_11$'157261', split_enc_11$'157270', split_enc_11$'157327', split_enc_11$'157339', split_enc_11$'157354',split_enc_11$'157381', split_enc_11$'157411', split_enc_11$'157432', split_enc_11$'157435', split_enc_11$'157438', split_enc_11$'157447', split_enc_11$'157456', split_enc_11$'157471', split_enc_11$'157474', split_enc_11$'157486', split_enc_11$'157489', split_enc_11$'157498', split_enc_11$'157549', split_enc_11$'157603', split_enc_11$'157621', split_enc_11$'157621', split_enc_11$'157639', split_enc_11$'157648', split_enc_11$'157663', split_enc_11$'157696', split_enc_11$'157837', split_enc_11$'157912', split_enc_11$'158350', split_enc_11$'742243848', split_enc_11$'742243852', split_enc_11$'742243854', split_enc_11$'154438', split_enc_11$'157246', split_enc_11$'152818')


#for every subject:
c = 0 
for (ssid in array(1:length(recall11_df))){
    i = sf11_by_sub[[ssid]]
    j = recall11_df[[ssid]]
    c = c +1 
    output  <- i %>% 
      mutate(recalls_final = tolower(word_enc) %in% tolower(j$V3))%>%  #matches the recall with task word
      mutate(recalls_final = case_when(recalls_final == "TRUE" ~ 1, #if recalled word, puts a 1 
                               recalls_final == "FALSE" ~ 0)) %>%  
      group_by(condition, trialcode) %>% 
      mutate(sum_recall = sum(recalls_final)) %>% # this column sums the recalls by condition and task
      group_by(blocknum) %>% 
      mutate(sum_recall_block = sum(recalls_final)) %>% #sums recalls by block
      group_by(trialcode) %>% 
      mutate(sum_recall_trialcode = sum(recalls_final)) #sums recalls just by task 
    if (c ==1) {
      sf11_total_final = output
    } else {
      sf11_total_final = rbind(sf11_total_final,output)
    }}

sf11_total_final 
```


```{r}
#recall by task 
library(dplyr)



sf11_total_2<- sf11_total_final %>% 
  group_by(subject) %>% 
  mutate(recall_percent2 = sum(recalls_final)/192*100) %>% 
  summarise(mean_rec = mean(recall_percent2, na.rm = TRUE))


#plot of each subjects recall in order 
sf11_total_2 %>% 
  ggplot(aes(x = reorder(as.character(subject), mean_rec), y = mean_rec))+
  geom_col(fill = "orchid", width = .8)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  labs(title    = "Percent of Total Words Recalled for each Subject",
         x        = "Subject Number",
         y        = "Percent Recalled")


mean_recall11_fin <- mean(sf11_total_2$mean_rec, na.rm = TRUE)
mean_recall11_fin


sd_11 <-sd(sf11_total_2$mean_rec, na.rm = TRUE)

```

```{r}
#means between same and novel

sf11_total_final_between<- sf11_total_final %>% 
  group_by(subject, between_condition) %>% 
  mutate(recall_percent2 = sum(recalls_final)/192*100) %>% 
  summarise(mean_rec = mean(recall_percent2, na.rm = TRUE))

sf11_total_final_between_same <- sf11_total_final_between %>% 
  filter(between_condition == "same")


mean_recall11_fin_same<- mean(sf11_total_final_between_same$mean_rec, na.rm = TRUE)
mean_recall11_fin_same


sf11_total_final_between_novel <- sf11_total_final_between %>% 
  filter(between_condition == "novel")

mean_recall11_fin_novel<- mean(sf11_total_final_between_novel$mean_rec, na.rm = TRUE)
mean_recall11_fin_novel


t.test(sf11_total_final_between_same$mean_rec, sf11_total_final_between_novel$mean_rec)

cohensD(mean_rec~ between_condition, sf11_total_final_between)
```




```{r}
#separate by between condition 
sf11_total_final2 <-sf11_total_final %>% 
  mutate(between_condition = case_when(blockcode == "control_mid_same" ~ "same",
                                         blockcode == "control_high_same" ~"same",
                                         blockcode == "high_control_same" ~"same",
                                         blockcode == "mid_control_same" ~"same",
                                       blockcode == "control_mid_novel" ~ "novel",
                                         blockcode == "control_high_novel" ~"novel",
                                         blockcode == "high_control_novel" ~"novel",
                                         blockcode == "mid_control_novel" ~"novel")) %>% 
  filter(task_switch == "switch" & condition == "high"|task_switch == "repeat" & condition == "high"|task_switch == "start" & condition == "high"| task_switch == "switch" & condition == "mid"| task_switch == "repeat" & condition == "mid"| task_switch == "start" & condition == "mid"|task_switch == "repeat" & condition == "cont_high"| task_switch == "start" & condition == "cont_high"| task_switch == "repeat" & condition == "cont_mid"| task_switch == "start" & condition == "cont_mid")


sf11_total_same_fin <- sf11_total_final2 %>% 
  filter(between_condition == "same")


sf11_total_novel_fin <- sf11_total_final2 %>% 
  filter(between_condition == "novel")
```


```{r}
model_condition_total_final_3w<- glmer(recalls_final~condition_mh*condition_control*between_condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_final2)
summary(model_condition_total_final_3w)

plot_model(model_condition_total_final_3w, type = "int")
```




```{r}
#SAME

#plot average recalls for task and condition

#separate control into high and mid paired 
#no switch items in the control 
#difference score error bars same

sf12_total_tally_same <- sf11_total_same_fin %>% 
  group_by(subject, condition) %>% 
  tally() 



sf12_total_same_fin2 <- sf11_total_same_fin %>% 
  dplyr:: select(subject, condition, trialcode, sum_recall, recalls_final) %>% 
  group_by(subject, condition) %>% 
  mutate(sum_recall2 = sum(recalls_final)) %>% 
  summarise(mean_rec_cond = mean(sum_recall2)) 

merged_same <- merge(sf12_total_same_fin2,sf12_total_tally_same)


merged_same_final<- merged_same %>% 
  mutate(prop_cond = mean_rec_cond/n)

difference_error_same_fin <- merged_same_final %>% 
  dplyr::select(subject, condition, prop_cond) %>% 
  reshape(idvar = "subject", timevar = "condition", direction = "wide") %>% 
  group_by(subject) %>% 
  mutate(diff_cont_high = sum(prop_cond.high- prop_cond.cont_high)) %>% 
  mutate(diff_cont_mid = sum(prop_cond.mid- prop_cond.cont_mid))




se_cont_high_same_fin <- std.error(difference_error_same_fin$diff_cont_high)

se_cont_mid_same_fin <- std.error(difference_error_same_fin$diff_cont_mid)


same_fin_df = data.frame(condition = c("control (mid)", "mid", "control (high)", "high"), n = c(41,41,41,41), mean = c(0.08960764, 0.08841463, 0.07741251, 0.08790650), standerr = c(0.009712275, 0.009712275, 0.008166214, 0.008166214),between_condition = c("same", "same", "same", "same"))

same_fin_df<- same_fin_df %>% 
  mutate(condition = fct_relevel(condition, "control (mid)", "mid", "control (high)", "high"))

fin_within_same <- same_fin_df %>% 
  ggplot(aes(x = condition, y = mean)) +
  geom_col(width = .7, aes(fill = condition), alpha = .8, color = "black", linewidth = .3) +
  labs(title    = "Percentage of Recalls by Condition",
         x        = "Condition",
         y        = "Percent Recalled")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=mean-standerr, ymax=mean+standerr))+
scale_y_continuous(labels = scales::percent_format(accuracy = 1L), expand = c(0,0))+
  scale_x_discrete(labels=c("control" = "Control","mid"= "Low Switch", "high" = "High Switch"))+
    scale_fill_manual(values = c("lightgreen", "green4", "lavender", "darkorchid4"))
```







```{r}
#model for the just same condition 

model_condition_same_11<- glmer(recalls_final~condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_same_fin)
summary(model_condition_same_11)


r2glmm::r2beta(model_condition_same_11, partial = TRUE)


model_condition_same_11_2<- glmer(recalls_final~condition_mh*condition_control +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_same_fin)
summary(model_condition_same_11_2)

plot_model(model_condition_same_11_2, type = "int")
```



```{r}
#NOVEL 

#plot average recalls for task and condition

#separate control into high and mid paired 
#no switch items in the control 
#difference score error bars novel 

sf11_total_tally_novel <- sf11_total_novel_fin %>% 
  group_by(subject, condition) %>% 
  tally() 



sf11_total_novel_fin2 <- sf11_total_novel_fin %>% 
  dplyr:: select(subject, condition, trialcode, sum_recall, recalls_final) %>% 
  group_by(subject, condition) %>% 
  mutate(sum_recall2 = sum(recalls_final)) %>% 
  summarise(mean_rec_cond = mean(sum_recall2)) 

merged_novel <- merge(sf11_total_novel_fin2,sf11_total_tally_novel)


merged_novel_final <- merged_novel %>% 
  mutate(prop_cond = mean_rec_cond/n)

difference_error_nov_fin <- merged_novel_final %>% 
  dplyr::select(subject, condition, prop_cond) %>% 
  reshape(idvar = "subject", timevar = "condition", direction = "wide") %>% 
  group_by(subject) %>% 
  mutate(diff_cont_high = sum(prop_cond.high- prop_cond.cont_high)) %>% 
  mutate(diff_cont_mid = sum(prop_cond.mid- prop_cond.cont_mid))



se_cont_high_nov_fin <- std.error(difference_error_nov_fin$diff_cont_high)

se_cont_mid_nov_fin <- std.error(difference_error_nov_fin$diff_cont_mid)


nov_fin_df = data.frame(condition = c("control (mid)", "mid", "control (high)", "high"), n = c(43,43,43,43), mean = c(0.08088979, 0.07655039, 0.08442872, 0.07170543), standerr = c(0.008895648, 0.008895648, 0.01091132, 0.01091132), between_condition = c("novel", "novel", "novel", "novel"))

nov_fin_df<- nov_fin_df %>% 
  mutate(condition = fct_relevel(condition, "control (mid)", "mid", "control (high)", "high"))

nov_fin_df %>% 
  ggplot(aes(x = condition, y = mean)) +
  geom_col(width = .7, aes(fill = condition), alpha = .8, color = "black", linewidth = .3) +
  labs(title    = "Percentage of Recalls by Condition",
         x        = "Condition",
         y        = "Percent Recalled")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=mean-standerr, ymax=mean+standerr))+
scale_y_continuous(labels = scales::percent_format(accuracy = 1L), expand = c(0,0))+
  scale_x_discrete(labels=c("control" = "Control","mid"= "Low Switch", "high" = "High Switch"))+
    scale_fill_manual(values = c("lightgreen", "green4", "lavender", "darkorchid4"))
```





```{r}
#model for the just novel condition 


sf11_total_novel_fin<- sf11_total_novel_fin %>% 
  mutate(condition = fct_relevel(condition, "high", "mid", "cont_high", "cont_mid"))

model_condition_novel_11<- glmer(recalls_final~condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_novel_fin)
summary(model_condition_novel_11)


r2glmm::r2beta(model_condition_novel_11, partial = TRUE)



sf11_total_novel_fin<- sf11_total_novel_fin %>% 
  mutate(condition = fct_relevel(condition, "high", "mid", "cont_high", "cont_mid"))

model_condition_novel_11_2<- glmer(recalls_final~condition_mh*condition_control +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_novel_fin)
summary(model_condition_novel_11_2)

```



```{r}

between_condition_bind_final_v1 <- rbind(same_fin_df, nov_fin_df)


between_condition_bind_final_v1 %>% 
  ggplot(aes(x = condition, fill = interaction(between_condition,condition), y = mean)) +
  geom_bar(position="dodge", stat="identity", color = "black", linewidth = .3, alpha = .8) +
  labs(title    = "Percentage of Recalls by Condition and Task",
         x        = "Condition",
         y        = "Percent Recalled")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=mean-standerr, ymax=mean+standerr))+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L), expand = c(0,0))+
  scale_x_discrete(labels=c("cont_mid" = "Control (Low)","mid"= "Low Switch", "cont_high" = "Control (High)", "high" = "High Switch"))+
  scale_fill_manual(name = "Condition", values=c("lightgreen", "lightgreen", "darkgreen", "darkgreen", "lavender", "lavender","darkorchid4", "darkorchid4")) +
  facet_wrap(.~between_condition)
```



```{r}
#model comparing same and novel 

model_condition_total_11<- glmer(recalls_final~condition*between_condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_final2)
summary(model_condition_total_11)

plot_model(model_condition_total_11, type = "int")



sf11_total_final2_high <- sf11_total_final2 %>% 
  filter(condition == "high"| condition == "cont_high")


model_condition_total_11<- glmer(recalls_final~condition*between_condition +list_half+blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_final2_high)
summary(model_condition_total_11)

r2glmm::r2beta(model_condition_total_11, partial = TRUE)


plot_model(model_condition_total_11, type = "int")

```





```{r}
#model 2x2 mid/high and switch/repeat 

sf11_total_final3<-sf11_total_final2 %>% 
  filter(condition == "high" | condition == "mid") %>% 
  filter(task_switch == "switch" | task_switch == "repeat")



#same

sf11_total_final_same_transition<-sf11_total_final2 %>% 
  filter(condition == "high" | condition == "mid") %>% 
  filter(task_switch == "switch" | task_switch == "repeat") %>% 
  filter(between_condition == "same")

model_transition_final_11_same<- glmer(recalls_final~condition*task_switch + list_half+(1|subject)+ (1|word_enc), family = binomial, data = sf11_total_final_same_transition)
summary(model_transition_final_11_same)


plot_model(model_transition_final_11_same, type = "int")

#novel 

sf11_total_final_nov_transition<-sf11_total_final2 %>% 
  filter(condition == "high" | condition == "mid") %>% 
  filter(task_switch == "switch" | task_switch == "repeat") %>% 
  filter(between_condition == "novel")

model_transition_final_11_novel<- glmer(recalls_final~condition*task_switch +list_half + blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_final_nov_transition)
summary(model_transition_final_11_novel)


plot_model(model_transition_final_11_novel, type = "int")


#total

model_transition_final_11<- glmer(recalls_final~condition*task_switch*between_condition +list_half + blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_final3)
summary(model_transition_final_11)


plot_model(model_transition_final_11, type = "int")


```



```{r}
#boundary vs preboundary- supplemental materials 



sf11_total_mid_spc_final<- sf11_total_final2 %>% 
  filter(condition == "mid") %>% 
  filter(trialnum == "5" | trialnum == "6" |trialnum == "8" |trialnum == "9" |trialnum == "10" |trialnum == "12"| trialnum == "13" |trialnum == "14"| trialnum == "16" |trialnum == "17" |trialnum == "18" |trialnum == "20") %>%
  mutate(trialnum_new = case_when(trialnum == "5" ~ "boundary",
                                  trialnum == "6" ~ "postboundary",
                               trialnum == "8" ~ "preboundary",
                               trialnum == "9" ~ "boundary",
                               trialnum == "10" ~ "postboundary",
                               trialnum == "12" ~ "preboundary",
                               trialnum == "13" ~ "boundary",
                               trialnum == "14" ~ "postboundary",
                               trialnum == "16" ~ "preboundary",
                               trialnum == "17" ~ "boundary",
                               trialnum == "18" ~ "postboundary",
                               trialnum == "20" ~ "preboundary")) 



spc_mid_11_tally_final <- sf11_total_mid_spc_final %>% 
  group_by(subject, trialnum_new) %>% 
  tally() 
spc_mid_11_tally_final


spc_mid_11_final <- sf11_total_mid_spc_final %>% 
  dplyr:: select(subject, trialnum_new, between_condition, recalls_final) %>% 
  group_by(subject, trialnum_new, between_condition) %>% 
  mutate(sum_recall2 = sum(recalls_final)) %>% 
  summarise(mean_rec_cond = mean(sum_recall2)) 


merged_spc_final <- merge(spc_mid_11_final,spc_mid_11_tally_final)


merged_spc_final <- merged_spc_final %>% 
  mutate(prop_cond = mean_rec_cond/n)


merged_spc_final<- merged_spc_final %>% 
  mutate(trialnum_new = fct_relevel(trialnum_new, "preboundary", "boundary", "postboundary"))


library(Rmisc)

spc_mid_11_final <- summarySEwithin(merged_spc_final, measurevar="prop_cond", withinvars = c("trialnum_new", "between_condition"),idvar = "subject", na.rm=FALSE, conf.interval=.95)


spc_mid_11_final %>% 
  ggplot(aes(x = trialnum_new, fill = interaction(between_condition,trialnum_new), y = prop_cond)) +
  geom_bar(position="dodge", stat="identity", color = "black", linewidth = .3, alpha = .8) +
  labs(title    = "Percentage of Recalls by Condition and Task",
         x        = "Transition Type",
         y        = "Percent Recalled")+
  theme_classic()+
  geom_errorbar(width=.1, position=position_dodge(.9), aes(ymin=prop_cond-se, ymax=prop_cond+se))+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L), expand = c(0,0))+
  scale_fill_manual(name = "Transition Type", values=c("grey60", "grey20", "darkseagreen2", "darkgreen", "grey60", "grey20","lavender", "darkorchid4")) +
  facet_wrap(.~between_condition)


```



```{r}
#model for boundary information 
detach(package:Rmisc) 
detach(package:plyr) #MUST RUN THIS

sf11_total_mid_spc_final<- sf11_total_mid_spc_final %>% 
  mutate(trialnum_new = fct_relevel(trialnum_new, "boundary", "preboundary", "postboundary"))


sf11_total_mid_spc_final2 <- sf11_total_mid_spc_final %>% 
  filter(between_condition == "novel")


sf11_total_mid_spc_3_model_total_final<- glmer(recalls_final~trialnum_new+ blocknum_contin + (1|subject)+ (1|word_enc), family = binomial, data = sf11_total_mid_spc_final2)
summary(sf11_total_mid_spc_3_model_total_final)

```


